Optimal (Multiway) Spatial Joins

### 2024-05-22 msj.tex
yufei

This section deals with a special version of the $k$-SJ problem. Recall that the input of $k$-SJ comprises $k$ sets of rectangles: $R_1, R_2, ..., R_k$. In the special version --- which we name the {\em H-V $k$-SJ} problem ---  we impose the constraints that (i) $k \ge 3$, (ii) $R_{k-1}$ should be a set of horizontal segments, and (iii) $R_k$ should be a set of vertical segments. For better clarity, we will represent the input sets as $R_1, R_2, ..., R_{k-2}, H$ ($=R_{k-1}$), and $V$ ($=R_k$). Remember that each $R_i$ ($i \in [k-2]$) is a set of rectangles. As we will see in the next section, solving the H-V $k$-SJ problem is an imperative step for settling the original $k$-SJ problem.

@@

\begin{lemma} \label{lmm:hv}
    The H-V $k$-SJ problem can be solved in 
    \myeqn{
        O(k) \cdot \big( F_{k-1}(n, \out) + n\log n + \out \big) \nn 
    }
    time using $O(n + \out + G_{k-1}(n, \out))$ space.
\end{lemma}

>>>>

This section deals with a special version of the $k$-SJ problem. Recall that the input of $k$-SJ comprises $k$ sets of rectangles: $R_1, R_2, ..., R_k$. In the special version --- which we name the {\em H-V $k$-SJ} problem ---  we impose the constraints that (i) $k \ge 3$, (ii) $R_{k-1}$ should be a set of horizontal segments, and (iii) $R_k$ should be a set of vertical segments. For better clarity, we will represent the input sets as $R_1, R_2, ..., R_{k-2}, H$ ($=R_{k-1}$), and $V$ ($=R_k$). Remember that each $R_i$ ($i \in [k-2]$) is a set of rectangles. As shown in the next section, solving the H-V $k$-SJ problem is an imperative step for settling the original $k$-SJ problem.

@@

\begin{lemma} \label{lmm:hv}
    The H-V $k$-SJ problem can be solved in 
    \myeqn{
        O(k) \cdot \big( F_{k-1}(n, \out) + n\log n + \out \big) \nn 
    }
    time using $O(n + \out) + G_{k-1}(n, \out)$ space.
\end{lemma}

\subsection{Categorizing the Result Tuples} \label{sec:hv:result-part}
